Scaffolder - Simple and reproducible genome scaffolding using text configuration files.

### 2011-01-13 text/src/article.tex
Further revise abstract

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of contigs. Therefore a common step in a genome project
  is piece separate contigs together and fill gaps generated by PCR. This
  scaffolding step, however, is non-trivial requiring manipulation of large
  blocks of nucleotide sequence. Manually joining contigs also hides the source
  of each region in the final genome fasta file. Taken together these
  considerations make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined "Scaffolder" is implemented in
  the ruby programming language and installed via the RubyGems software
  management system. Genome scaffolds are defined using YAML - a markup
  language, which is both human and machine-readable. Command line binaries and
  extensive documentation are also available for the package.

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent contigs using a relatively simple to write and edit
  scaffold file syntax. This scaffold file defines where each contig is used
  making the genome build reproducible and comparatively easier to edit than
  fasta sequence. This syntax also supports adding inserts to the scaffold for
  the purpose of bridging gaps or replace regions.

>>>>

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of contigs. Therefore a common step in a genome project
  is to join neighbouring sequence regions together and fill gaps using insert
  data generated through PCR. This scaffolding step, however, is non-trivial
  and requires manually editing large blocks of nucleotide sequence. Joining
  sequence contigs together also hides the source of each region in the final
  genome sequence. Taken together, these considerations may make reproducing or
  editing an existing genome build difficult.

  \paragraph*{Methods:} The software outlined "Scaffolder" is implemented in
  the Ruby programming language and can be installed via the RubyGems software
  management system. Genome scaffolds are defined using YAML - a markup
  language, which is both human and machine-readable. Command line binaries and
  extensive documentation are provided.

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent contigs using a relatively simple to write and edit
  scaffold file syntax. The Scaffolder syntax further allows inserts to be
  added to the scaffold for the purpose of filling unknown sequence regions.
  Defining the genome construction in a file makes the scaffolding process
  reproducible and comparatively easier to edit than raw fasta sequence.
